---
title: "four months"
author: "Daniel"
date: "2020/12/7"
output:
  html_document: default
  pdf_document: default
---



# Background

This application is **not** for makers. Here what i am trying to do is scoring a item of a brand given a subcategory. 

i guess that there is a correlation between social media data and alibaba number of vol for a item. so i take vol number from alibaba, and get social media data from two platforms **wei bo**、**xiao hong shu**.



## data 

time interval : [2020-06,2020-08] (3 months)

```{r}

xiaohongshu_6_8 <- read.csv("C:/Users/Daniel Kang/Desktop/xiaohongshu6_8.csv",T, encoding = "UTF-8")
weibo_6_8       <- read.csv("C:/Users/Daniel Kang/Desktop/weibo6_8.csv",T, encoding = "UTF-8")
colnames(weibo_6_8) <- c("index", "brands", "nations", "num_item", "vol", "revenue", "avg_price", "num_post", "plat_add", "trans", "reply", "likes")
colnames(xiaohongshu_6_8) <- c("index", "brands", "nations", "num_item", "vol", "revenue", "avg_price", "num_post", "plat_add", "saved", "reply", "likes", "trans")
weibo_6_8       <- weibo_6_8 %>% filter(num_post >= 10)
xiaohongshu_6_8 <- xiaohongshu_6_8 %>% filter(num_post >= 20)
glimpse(xiaohongshu_6_8)
glimpse(weibo_6_8)

```


## first regression: weibo only

varibales : y = log(vol)
            x = avg_price, num_item, trans, likes
**note**: $x_i$ all from weibo data

we can see the result below, trans and likes are statistically significant.
            
```{r}
summary(lm(log(weibo_6_8$vol) ~ scale(avg_price) + scale(num_item) +  scale(trans) + scale(likes), data = weibo_6_8))

```

## second regression : only xiao hong shu data

i tried different combinations of $x_i$, the coef is not significant statistically.
```{r}

summary(lm(log(xiaohongshu_6_8$销售数量) ~ scale(avg_price) + scale(num_item)  + scale(saved), 
           data = xiaohongshu_6_8))


```


## third regression : only weibo but for luxury brands

here, the trans and likes are significant, but the beta of likes is negative.
```{r}

weibo_6_8_high <- weibo_6_8 %>% filter(avg_price > 200) 
lm_6_8_high    <- lm(log(vol) ~ avg_price + num_item +  trans + likes, data = weibo_6_8_high)
summary(lm_6_8_high)




```

## forth regression : only weibo , but cheap brands

it is less significant than luxury brands
```{r}
weibo_6_8_cheap <- weibo_6_8 %>% filter(avg_price <= 200)
lm_6_8_cheap <- lm(log(vol) ~ avg_price + num_item +  trans + likes, data = weibo_6_8_cheap)
summary(lm_6_8_cheap)

```


## 5th regression :only xiao hong shu , but luxury brands

```{r xiaohongshu}
xiaohongshu_6_8_high <- xiaohongshu_6_8 %>% filter(avg_price > 200)
lm_6_8_high_xiaohongshu <- lm(log(vol) ~ avg_price + num_item + likes + num_post, data = xiaohongshu_6_8_high)
summary(lm_6_8_high_xiaohongshu)


```

## 5th regression :only xiao hong shu , but luxury brands

no big diff from above

```{r}

xiaohongshu_6_8_cheap <- xiaohongshu_6_8 %>% filter(avg_price <= 200)
lm_6_8_cheap_xiaohongshu <- lm(log(vol) ~ avg_price + item  + likes + saved + num_post, data = xiaohongshu_6_8_cheap)
summary(lm_6_8_cheap_xiaohongshu)

```


## 6th regression : data from both weibo & xiao hong shu

put weibo data and xiao hong shu data together, this regression involves **"likes"** from weibo, **"saved"** from xiao hong shu.

both of them are statistically significant.

```{r}

weibo_xiaohongshu_6_8 <- right_join(weibo_6_8, xiaohongshu_6_8, by = "brands")[-c(28,29),]
summary(lm(log(vol.x) ~ avg_price.x + num_item.x  + likes.x + saved , data = weibo_xiaohongshu_6_8))


```

## 7th regression : both data but luxury

less significant

```{r}
weibo_xiaohongshu_6_8_high <- weibo_xiaohongshu_6_8 %>% filter(avg_price.x > 200)
summary(lm(log(vol.x) ~ avg_price.x + num_item.x  + likes.x + saved  , data = weibo_xiaohongshu_6_8_high))


```



## 8th regression : both data but cheap brands

its not significant

```{r}
weibo_xiaohongshu_6_8_cheap <- weibo_xiaohongshu_6_8 %>% filter(avg_price.x <= 200)
summary(lm(log(vol.x) ~ avg_price.x + num_item.x  + likes.x + saved  , data = weibo_xiaohongshu_6_8_cheap))
```




# conclu

from the results above , i found that the data from weibo has more impact on vol data. but here i could have add more variables, like : attr, brands nation, the number of each topic in weibo or xiao hong shu(using LDA method) and so on.

again, this is not for makers. this is for the people who resell the cosme. i think it might be helpful if there is a score, and people can see the number from different dimention. and they can decide whether or not to buy this brand of a given subcategory.




















